Models of Lambek calculus enriched with subexponentials

### 2019-03-09 PaperDraft.tex
updates

Example:

\begin{itemize}
Let us show that $\mathcal{Q} \models !A \rightarrow A$.

Let $\mathcal{Q} \models !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$,
but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \models A$.

@@

Let $\langle a, b \rangle \models !A$. Let us show that $\langle a, b \rangle \models !!A$.

So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models A$.

Let $S' \subseteq S_{\langle a, b \rangle}$, then for each $\langle a', b' \rangle \in S', \langle a', b' \rangle \Vdash A$,
so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
\end{itemize}

@@

  Let $\langle A \rangle$
\end{theorem}

  Let $\mathcal{Q}$ be a relational quantale, then $Log(\mathcal{Q}) = L^{*}(\backslash, /, \bullet, {\bf 1}, \&, \vee)$.
\end{theorem}

>>>>

Let $\mathcal{R}$ be any R-model:

\begin{itemize}
  \item $\mathcal{R} \models !A \rightarrow !!A$;
  \item $\mathcal{R} \models !A \rightarrow A$.
\end{itemize}

\begin{enumerate}
\item Let us show that $\mathcal{Q} \Vdash !A \rightarrow A$.

Let $\mathcal{Q} \Vdash !A$ and $v$ be a valuation, hence $\langle a, b \rangle \Vdash !A$.
Hence there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$,
but $\langle a, b \rangle \in S_{\langle a, b \rangle}$, so $\langle a, b \rangle \Vdash A$.

@@

Let $\langle a, b \rangle \Vdash !A$. Let us show that $\langle a, b \rangle \Vdash !!A$.

So there exists $S_{\langle a, b \rangle} \subseteq \mathcal{Q}$,
such that $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \Vdash A$.

Let $S' \subseteq S_{\langle a, b \rangle}$, then for each $\langle a', b' \rangle \in S', \langle a', b' \rangle \Vdash A$,
so $\forall \langle a', b' \rangle \in S_{\langle a, b \rangle}, \langle a', b' \rangle \models !A$, so  $\langle a, b \rangle \models !!A$.
\end{enumerate}
\end{proof}

\begin{theorem} Soundness

  Let $\mathcal{R}$ be a class of $R$-frames, then $Log(\mathcal{R}) = L^{*}_{\bf 1} A_{\bf S 4}$
\end{theorem}

Modal cases follows from the previous lemma.
\end{proof}

  Let $W : Fm \to 2^R$, s.t. $W(A) = \{ \langle a, b \rangle \: | \: \mathcal{F}, \langle a, b \rangle \}$, then:
  \begin{enumerate}
    \item For each $A \in Fm$, $W(A)$ is a subrelation of $R$;
    \item
    \begin{enumerate}
      \item $W(A \backslash B) = \bigcup \{ \}$
      \item $W (A / B) = $
      \item $W (A \circ B) = $
      \item $W ({\bf 1}) = $
      \item $W (A \lor B) =$
      \item $W (A \land B) = $
    \end{enumerate}
  \end{enumerate}

\end{theorem}

\begin{defin} Algebra generated by $R$-frame.
\end{defin}

  Any relational quantale is isomorphic to some algebra generated by $R$-frame.
\end{theorem}

\begin{theorem}
\end{theorem}

  If $\Gamma \models_{R} A$, then $L^{*}_{\bf 1} A_{\bf S 4} \vdash \Gamma \rightarrow A$.
\end{theorem}

\begin{proof}
\end{proof}

@@

\end{theorem}
